A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 6_validation.tex
Tim: redo accuracy, uniformity and smoothness discussion and figures

We compare the total area (in \si{\milli\meter\squared}) of these overfill and underfill shapes to the total area of the boundary for each sample in the data set.
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.

@@

\subsubsection{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to produce.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths may cause the extruded material to bulge upwards instead of filling the required width.
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per scheme.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of the inward distributed and evenly distributed schemes is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less and infrequently from the nominal bead width compared to the other schemes.
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the evenly distributed scheme more often extrudes widths that deviate from the nominal width.

\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive extrusion segments generated by each scheme.
The relative frequency of these angles is shown in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
The inward distributed scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.

>>>>

We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in see \cref{over_underfill}.
The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.

@@

\subsubsection{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult to produce;
too narrow beads might result in fluttered extrusion and too wide beads might require a pressure in the nozzle beyond the specifications of the machine or they might bulge upward on the sides.
Moreover, bead widths deviating from the preferred bead width by a large amount may be hard to realize and may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.

To evaluate the uniformity of the width,
we calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.

\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We therefore measured the angle between consecutive extrusion segments generated by each scheme
and report on the occurence of each angle in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
We observe that compared to the naive method our framework produces less acute angles, but more obtuse angles.
The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.
